Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-01-26 GECCO/volunteer-clouds-gecco16.tex
Eliminating unneeded references
Acknowledgements commented for double-blind. References #95

Nowadays there is a big and increasing number of
distributed evolutionary computation software frameworks available on
the market, usually as open source frameworks \cite{Parejo12Survey}. 
Most of these frameworks have 
two features: they are {\em desktop} applications, that is, they must
be compiled or run directly on the operating system layer and, second,
they assume that the nodes that are going to run the system are under
the control of developers or they at least have access to them. In
fact, these features are commonly found in most soft computing
frameworks \cite{7094263}.

@@

%---------------------------------------------------------------
\section*{Acknowledgment}

This work has been supported in part by
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR), 
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico) and PYR-2014-17
GENIL project (CEI-BIOTIC Granada). Additional support was recieved by
Projects 5622.15-P (ITM) and  PROINNOVA 2015: 220590 (CONACYT).
We would also like to thank the
anonymous reviewers of previous versions of this paper who have really
helped us to improve 
this paper (and our work) with their suggestions. We are also grateful
to Anna S\'aez de Tejada for her help with the data processing scripts.

>>>>

Nowadays there is a big and increasing number of
distributed evolutionary computation software frameworks available on
the market, usually as open source frameworks \cite{Parejo12Survey}. 
Most of these frameworks have 
two features: they are {\em desktop} applications, that is, they must
be compiled or run directly on the operating system layer and, second,
they assume that the nodes that are going to run the system are under
the control of developers or they at least have access to them.

@@

%---------------------------------------------------------------
% \section*{Acknowledgment}
% 
% This work has been supported in part by
% TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR), 
% SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico) and PYR-2014-17
% GENIL project (CEI-BIOTIC Granada). Additional support was recieved by
% Projects 5622.15-P (ITM) and  PROINNOVA 2015: 220590 (CONACYT).
% We would also like to thank the
% anonymous reviewers of previous versions of this paper who have really
% helped us to improve 
% this paper (and our work) with their suggestions. We are also grateful
% to Anna S\'aez de Tejada for her help with the data processing scripts.
